\chapter{Introduction}

\section{Course Purpose and Learning Objectives}

This introductory chapter explains how the \textbf{Applied Physics in Industrial Design (APID)} project will run, what your team is expected to deliver, and how the hydroponics theme connects design work to applied physics. In this session, you will review the course workflow, assessment structure, teamwork expectations, and support resources before moving into later technical sessions.

By the end of this introduction, you should be able to:
\begin{enumerate}
    \item explain the purpose of the APID project and its project-based learning approach;
    \item describe why hydroponics agriculture is the shared project theme for the semester;
    \item identify the main deliverables, submission routes, and assessment formats used in the module; and
    \item organise your team so that weekly tasks, records, and communication remain manageable throughout the semester.
\end{enumerate}

Table~\ref{tab:session0-key-terms} defines the main terms used throughout this chapter.

\begin{table}[htbp]
\centering
\caption{Key terms introduced in the APID orientation}
\label{tab:session0-key-terms}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\textwidth}{|>{\raggedright\arraybackslash}p{0.2\textwidth}|X|}
\hline
\textbf{Term} & \textbf{Definition} \\
\hline
APID & Applied Physics in Industrial Design, the course that combines product development practice with applied physics reasoning. \\
\hline
Hydroponics agriculture & A method of growing plants without soil by controlling water, nutrients, support structures, and environmental conditions. \\
\hline
LLM & Large Language Model, a generative artificial intelligence tool that can assist with drafting, summarising, or brainstorming but must be checked critically. \\
\hline
CLO & Course Learning Outcome, the formal learning outcome used to structure assessment tasks. \\
\hline
ITEL & Institutional Teaching and E-Learning platform, the university system used for announcements, submission links, and updated deadlines. \\
\hline
PD & Product development, the structured process of turning an opportunity into a product concept, evaluation plan, and communication package. \\
\hline
\end{tabularx}
\end{table}

\section{Project Theme: Hydroponics Agriculture}


This year mark the third time APID has been offered. Previously, the module used a more open-ended project theme, which allowed for a wide variety of product ideas. However. the open theme also made it difficult for students to find a common context for applied physics concepts, and it led to some confusion about how to connect design work to technical reasoning. To address these issues, the project theme is now focused on hydroponics agriculture, which provides a shared context for all teams while still allowing for creativity and diversity in product ideas. 

Therefore, your team will propose a product related to hydroponics agriculture. The product may operate directly inside a hydroponic system or support hydroponic users, growers, or maintenance workflows.

Just to reiterate, hydroponics is a suitable project theme because it requires you to consider several applied physics topics at the same time, not limited to but including:
\begin{itemize}
    \item fluid transport and pressure losses in nutrient delivery systems;
    \item heat transfer and environmental control for plant growth;
    \item sensing and instrumentation for pH, electrical conductivity, temperature, or flow monitoring; and
    \item materials selection, structural stability, and manufacturability for safe, durable products.
\end{itemize}

The theme therefore keeps the project grounded in industrial design while still demanding technical reasoning. Your task is not merely to propose a visually interesting idea. You are expected to justify why the concept should work, who it serves, and how it can be developed systematically.

\section{Team Formation, Roles, and Working Method}

Teams are assigned by the module convenor, usually with four or five students per group. Random grouping is used to create diversity of experience and to simulate professional collaboration with unfamiliar teammates.

Once the group list is published on ITEL, review it immediately. If your name is missing, if you are an exchange student without an assigned team, or if a listed member is no longer attending the module, contact the module convenor as soon as possible.

Each group should appoint a group leader. To be fair, the group leader should be rotated every one or two week. The group leader will play a management role in addition to their normal work as a group member. This includes ensuring that everyone is involved, that work is divided fairly, that tasks are completed on time, and that nothing is forgotten in the project. The group leader does not have to make all the decisions, but they do have a responsibility to ensure that the group works effectively as a whole. They should also ensure that everyone is pulling in the same direction and that the project progresses according to plan. Ultimately, the group leader is responsible for ensuring that the project goals are achieved and that the prescribed deadlines are met.
Once you are assigned to a project team, you should remain to stay in the team for the entire term.

\section{Weekly Workflow and Meeting Expectations}

All sessions contain a \textbf{pre-class task}, and a \textbf{in-class task}. 

Pre-class activities, are mean the activity that need to be conducted by each of the member prior attending the tutorial Session. This activities are designed to help you prepare for the tutorial discussion and to make progress on the project. They may include reading, research, calculations, or drafting outputs that will be discussed in class. The tutorial discussion is an opportunity to share your work, receive feedback from peers and the lecturer, and identify areas for improvement. 

The \textbf{in-class task} is the activity that conducted during the tutorial session. During the tutorial session, you will compare ideas, receive feedback, and identify what must be improved. After class, your team should refine the material so that it can be used in later deliverables.

It also possible that group conduct meetings outside of class time. The meetings will normally be held in a mutually convenient location in the school, or elsewhere on campus, and have no prescribed time limit. What goes on at these meetings is completely up to the group, but they are usually more informal in nature. There is no requirement for a chairperson or minutes, but some groups may find it useful to carry on with these practices here.



\section{Deliverables and Assessment Overview}

Table~\ref{tab:session0-deliverables} summarises the major deliverables introduced in this chapter. Exact dates, upload links, and any weighting updates must always be confirmed through ITEL.

\begin{table}[htbp]
\centering
\caption{Major APID deliverables introduced in Session 0}
\label{tab:session0-deliverables}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\textwidth}{|>{\raggedright\arraybackslash}p{0.2\textwidth}|>{\raggedright\arraybackslash}p{0.18\textwidth}|>{\raggedright\arraybackslash}p{0.2\textwidth}|X|}
\hline
\textbf{Deliverable} & \textbf{Typical timing} & \textbf{Submission format} & \textbf{Purpose} \\
\hline
Weekly tutorial exercises & Throughout the semester & PDF or lecturer-specified format via ITEL & Documents your team's progress in needs analysis, specifications, concept generation, and related development tasks. \\
\hline
Practical test components & Selected tutorial sessions & Tutorial files submitted to the relevant weekly ITEL tabs & Demonstrates your individual understanding and contribution through graded tutorial outputs. \\
\hline
Fishbowl assessment & Later in the semester & Live discussion in class & Assesses your ability to explain, defend, and connect design decisions to the group project. \\
\hline
Presentation day & End-of-semester presentation period & Slides, optional demonstration material & Communicates the problem, proposed solution, and reflective learning outcomes to the class. \\
\hline
Multimedia report & After concept development activities & Video file or upload link via ITEL & Shows concept alternatives, concept selection rationale, and planned next steps. \\
\hline
Final report & End of semester & Single group PDF via ITEL & Integrates the full product development process into one self-contained technical report. \\
\hline
\end{tabularx}
\end{table}

\section{Resources, Support, and Project Constraints}

This section highlights the practical constraints that affect the project. The module does not provide a dedicated project budget, so teams should choose scopes and materials realistically. If your concept requires prototype expenses, those costs must be managed by the team unless a different arrangement is approved by the lecturer.

\section*{Intellectual Property Rights}

In this course, any inventions made by your team will usually belong to you. If you decide to apply for a patent to protect your invention, you can either do it by yourself and pay all related costs, or you can choose to patent it with the help of Universiti Malaysia Sabah. In this case, the university will take care of all expenses and other necessary steps. However, it's important to discuss and agree with your team members early on about how to divide any earnings from your invention. Also, any ideas shared on a digital whiteboard or similar tool should be considered as recorded evidence of how your invention developed over time.


