\section{Multimedia Report}

The multimedia report asks your group to communicate concept development in a concise visual format. Prepare a video of no more than 10 minutes and use English as the primary language of communication.

\subsection{Required Content}

Your video should include the following elements:
\begin{itemize}
    \item First, display all the concept sketches you developed during the "Concept Generation" activity.
    \item  Clearly explain the reasons and criteria for selecting the top concepts. 
    \item Assume the course can be extended for a few more months. In this hypothetical scenario, briefly explain your approach and methodology for the concept testing process. 
    \item Highlight the importance of applying for patent protection. Explain why it is essential for your concepts to be patented and detail your plan for applying for patent protection. This should include the steps you would take and any important considerations.
\end{itemize}

\subsection{What will be graded}

Ensure your video is well-edited, with smooth transitions and no technical issues. Use creative
elements, such as animations and engaging visuals, to make your presentation more captivating.
Maintain a clear and logical flow throughout the video, with smooth transitions between each
section. To gain extra mark, you are encourage to show a deep understanding of related to the concepts,
providing insightful explanations and showing thorough preparation. Follow these instructions
carefully to maximize your marks on the multimedia report.

\subsection{Submission Guidance}

Upload the final video to Youtube video hosting. Name the video file as Group X - The Name of Your Concept. For example, if your group is Group 1 and your concept is called "Smart Water Bottle", the video file should be named "Group 1 - Smart Water Bottle". After uploading, share the video link to the Excel, under the Tab "Video Links", and also submit the link to ITEL.

Make sure set the video privacy to "Public" so that the lecturer can access it without any issues. If you have any questions about the submission process, please contact the me for assistance.



