\section{Golden Rules for Group Projects}

The purpose of these rules is to keep the project manageable, fair, and professionally documented. They are based on common weaknesses seen in previous student projects.

\begin{itemize}
    \item \textbf{Work consistently from the start.} APID is a three-credit module, so steady weekly effort is expected. Early progress reduces deadline pressure and improves the quality of design decisions.
    \item \textbf{Contribute visibly and responsibly.} Do not wait passively for work to be assigned. Teams function better when members volunteer, communicate progress, and support shared goals.
    \item \textbf{Use suitable collaboration tools.} Shared folders, version control, and structured note-taking help teams avoid duplicated effort and lost files.
    \item \textbf{Protect time for writing and revision.} A strong idea is not enough on its own; your grades also depend on how clearly the work is documented and justified.
    \item \textbf{Monitor progress across the full team.} If one part of the work is delayed, the whole project is affected. Regular check-ins help teams identify problems early.
    \item \textbf{Treat meetings as working sessions.} Good meetings clarify decisions, allocate tasks, and remove uncertainty. Most project progress, however, still happens between meetings.
    \item \textbf{Keep reliable records.} Minutes, action lists, and shared evidence make it easier to track decisions, resolve disputes, and prepare the final report.
\end{itemize}
