

\begin{landscape}
\begin{footnotesize}
\begin{longtable}{|c|p{4cm}|p{5cm}|c|p{6.5cm}|}
\caption{Bicycle Suspension Needs, Metrics, Units, and Justification} \label{table:bicycle_need_metric_unit_justification} \\
\hline
\textbf{No} & \textbf{Need} & \textbf{Metric} & \textbf{Units} & \textbf{Justification} \\
\hline
\endfirsthead

\multicolumn{5}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\textbf{No} & \textbf{Need} & \textbf{Metric} & \textbf{Units} & \textbf{Justification} \\
\hline
\endhead

\hline \multicolumn{5}{r}{\textit{Continued on next page}} \\
\endfoot

\hline
\endlastfoot

\multirow{3}{*}{1} 
  & \multirow{3}{4.5cm}{Reduces vibration to the hands} 
    & 1. Attenuation from dropout to handlebar at 10\,Hz & dB & High-frequency vibrations are most noticeable at the hands; reduction improves rider comfort. \\
\cline{3-5}
  & & 2. Maximum value from the Monster & g & Captures peak impact events to evaluate suspension performance. \\
\cline{3-5}
  & & 3. Minimum descent time on test track & s & Demonstrates performance under real trail conditions. \\
\hline
2 & Allows easy traversal of slow, difficult terrain 
  & 1. Spring preload & N & Adjustability of preload helps with traction and control on rough, slow trails. \\
\hline
\multirow{3}{*}{3} 
  & \multirow{3}{4.5cm}{Enables high-speed descents on bumpy trails} 
    & 1. Attenuation from dropout to handlebar at 10\,Hz & dB & Reducing vibration at high speeds helps maintain control and comfort. \\
\cline{3-5}
  & & 2. Maximum value from the Monster & g & Measures extreme shock loads during descents. \\
\cline{3-5}
  & & 3. Minimum descent time on test track & s & Indicates efficiency and capability over fast, bumpy terrain. \\
\hline
4 & Allows sensitivity adjustment 
  & 1. Damping coefficient adjustment range & N$\cdot$s/m & Provides tunability for rider preference and terrain type. \\
\hline
5 & Preserves the steering characteristics of the bike 
  & 1. Maximum travel (26-in. wheel) & mm & Excessive suspension travel can affect geometry and handling. \\
\hline
\multirow{2}{*}{6} 
  & \multirow{2}{4.5cm}{Remains rigid during hard cornering} 
    & 1. Spring preload & N & A stiffer spring resists compression and maintains geometry. \\
\cline{3-5}
  & & 2. Lateral stiffness at the tip & kN/m & Prevents lateral flexing which would impair handling under load. \\
\hline
7 & Is lightweight 
  & 1. Total mass & kg & Lower mass improves bike efficiency and handling. \\
\hline
8 & Provides stiff mounting points for the brakes 
  & 1. Lateral stiffness at brake pivots & kN/m & Ensures braking forces do not deform the frame and affect control. \\
\hline

\end{longtable}
\end{footnotesize}
\end{landscape}